---
title: "Essay analysis"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
Here we will perform analysis of LIWC data of essays, written by different groups of people.

```{r}
install.packages(c("tidyverse", "dplyr", "ggplot2", "ggpubr", "coin", "rstatix"))
```


```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(coin)
library(rstatix)
```

First, let's load the data. Concatenated dataset is in ```all_groups.csv```

```{r}
data <- read.csv("https://raw.githubusercontent.com/Rexhaif/hse-lingdata-project/main/all_groups.csv")
data[data == 0] <- NA
head(data)
```
This is concatenation of LIWC analysis using LIWC2015 + default russian dictionary. There is a lot of columns representing different word categories, but we only need those related to emotiona expression.

```{r}
needed_columns <- c("Filename", "group", "Позитив", "Негатив", "Беспокойство", "Гнев", "Грусть")
data <- data[, needed_columns]
head(data)
```

Also, let's rename the columns for convenience.
```{r}
columns <- c("file", "group", "Positive", "Negative", "Anxienty", "Anger", "Sadness")
emotion_columns <- c("Positive", "Negative", "Anxienty", "Anger", "Sadness")
colnames(data) <- columns
```

Next, we will perform some exploratory analysis, checking what we are working on.
```{r}
group_by(data, group) %>%
  summarise(
    count = n(),
    across(
      emotion_columns,
      list(
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE),
        median = ~ median(.x, na.rm = TRUE)
      )
    )
  )
```
So, in general values have high SD + due to liwc limitations. Let's display the same information in a visual way.
```{r}
for(col in emotion_columns) {
  ggboxplot(
    data, 
    x = "group", y = col, 
    color = "group",
    ylab = col, xlab = "Group"
  )
  ggsave(
    paste("plots/boxplots/", col, ".pdf", sep='')
  )
}
```

We need to examine the distribution of values overall and inside each group. Let's do it by looking at histogram, Q-Q plot + performing Shapiro Wilk's test.
```{r}
for(col in emotion_columns) {
  ggqqplot(
    get(col, data),
    title=paste("Q-Q plot for ", "Positive", sep='')
  )
  ggsave(
    paste("plots/qqplots/", col, ".pdf", sep='')
  )
}
```
Our data partially fits Q-Q plot theoretical part, so it may be normal distribution. But there is also some deviations. Guess we need to look at histograms.

```{r}
for(col in emotion_columns) {
  ggplot(data, aes_string(x=col)) +
    geom_histogram(
      aes(y=..density..),
      position="identity",
      colour="black", fill="white",
      alpha=0.5
    ) +
    geom_density(alpha=0.2, fill="#FF6666")
  ggsave(
    paste("plots/histogram/", col, ".pdf", sep="")
  )
}
```
By looking at histograms, we can say that some of our categories are more likely to be from exponential distribution(Anger, Anxiety, Sadness) and some are more likely ot be from Normal distribution(Positive, Negative). Probably it is save to say that our data generally do not come from normal distribtuion, but additionally, we will perform Shapiro-Wilk test to check of any values are `normal` enough. We will use $\alpha = 0.001$ as our significance level.

```{r}
for(col in emotion_columns) {
  print("=============================")
  print(col)
  print(shapiro.test(get(col, data)))
}
```

As none of the tests returned p-value > $\alpha = 0.001$, we do reject Null hypothesis(which states that our data comes from normal distribution).

# Let's move into actual hypothesis testing

Mainly we want to learn if any of groups of people used emotional words differently(more or less frequently) than the control group. And if this is true, we want to know the groups and confidence interval of medians of values.

Firstly, we will check if the effect(using emotional wording differently among groups) is present at all. For this, the Kruskal-Wallis test to be used. For this test the null hypothesis is that parameter distribution is the same for every group. We will use significance level of $\alpha = 0.1$.

```{r}
for(col in emotion_columns) {
  formula <- paste(col, "~ group")
  print("=====================================================")
  print(formula)
  print(kruskal.test(as.formula(formula), data = data, na.action = na.exclude))
}
```

Only for Anger word category the kruskal test p-value is less than significance level. That means that in our data the effect is present only for Anger. Let's apply pairwise Wilcoxon(Mann-Whitney) test to see which groups are different. Significance level remains the same: $\alpha = 0.1$.

```{r}
data %>% pairwise_wilcox_test(
  Anger ~ group,
  p.adjust.method = "BH",
  ref.group = "control"
)
```

As we see, we can reject null-hypothesis for Mann-Whitney test for following pairs:
- Clinic / Control
- Soc / Control

Let's estimate effect_size:

```{r}
control_clinic = data %>% filter(group == "control" | group == "clinic")
control_soc = data %>% filter(group == "control" | group == "soc")
control_psy = data %>% filter(group == "control" | group == "psy")
control_stem = data %>% filter(group == "control" | group == "stem")
print(wilcox_effsize(control_clinic, Anger ~ group))
print(wilcox_effsize(control_soc, Anger ~ group))
print(wilcox_effsize(control_psy, Anger ~ group))
print(wilcox_effsize(control_stem, Anger ~ group))
```

Finally, we will compute CI of medians in each group:

```{r}
control = data %>% filter(group == "control")
clinic = data %>% filter(group == "clinic")
soc = data %>% filter(group == "soc")
print("Control")
print(wilcox.test(control$Anger, conf.int = TRUE, conf.level = 0.95)$conf.int)
print("Clinic")
print(wilcox.test(clinic$Anger, conf.int = TRUE, conf.level = 0.95)$conf.int)
print("Soc")
print(wilcox.test(soc$Anger, conf.int = TRUE, conf.level = 0.95)$conf.int)

```




