---
title: "Essay analysis"
output: html_notebook
---
Here we will perform analysis of LIWC data of essays, written by different groups of people.

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggpubr)
```

First, let's load the data. Concatenated dataset is in ```all_groups.csv```

```{r}
data <- read.csv("./all_groups.csv")
data[data == 0] <- NA
head(data)
```
This is concatenation of LIWC analysis using LIWC2015 + default russian dictionary. There is a lot of columns representing different word categories, but we only need those related to emotiona expression.

```{r}
needed_columns <- c("Filename", "group", "Позитив", "Негатив", "Беспокойство", "Гнев", "Грусть")
data <- data[, needed_columns]
head(data)
```

Also, let's rename the columns for convenience.
```{r}
columns <- c("file", "group", "Positive", "Negative", "Anxienty", "Anger", "Sadness")
emotion_columns <- c("Positive", "Negative", "Anxienty", "Anger", "Sadness")
colnames(data) <- columns
```

Next, we will perform some exploratory analysis, checking what we are working on.
```{r}
group_by(data, group) %>%
  summarise(
    count = n(),
    across(
      emotion_columns,
      list(
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE),
        median = ~ median(.x, na.rm = TRUE)
      )
    )
  )
```
So, in general values have high SD + due to liwc limitations. Let's display the same information in a visual way.
```{r}
for(col in emotion_columns) {
  ggboxplot(
    data, 
    x = "group", y = col, 
    color = "group",
    ylab = col, xlab = "Group"
  )
  ggsave(
    paste("plots/boxplots/", col, ".svg", sep='')
  )
}
```

We need to examine the distribution of values overall and inside each group. Let's do it by looking at histogram, Q-Q plot + performing Shapiro Wilk's test.
```{r}
for(col in emotion_columns) {
  ggqqplot(
    get(col, data),
    title=paste("Q-Q plot for ", "Positive", sep='')
  )
  ggsave(
    paste("plots/qqplots/", col, ".svg", sep='')
  )
}
```








